---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ggecon)](https://CRAN.R-project.org/package=ggecon)
<!-- badges: end -->


## Pre-Installation Steps and System Requirements

### Installing node.js

### Installing parlance

### Creating a Parler Profile and Obtaining Cookies

Disclaimer: The end user uses this piece of software at their own legal responsibility. The authors do not take any responsibility for how you use the piece of software. We do not encouragement the breach of Terms of Service of any company, except in legally and ethically permitted cases. 

## Installation and Loading

```{r eval = F}
devtools::install_github("schliebs/parleR")
```

```{r message = F,warning = F}
library(parleR)
```

```{r}
library(tidyverse)
```


## API Authentication

There are two options to set a CT API token and save it in the system environment. The first one is to trigger an RStudio window opening, and entering the token.

## Get Posts by Username

```{r,message = F,warning = F}
post_df1 <- 
  parler_posts(user = "Grenell",
               output_format = "data.frame",
               flatten_sep = " || ",
               parse_numbers = TRUE,
               verbose = TRUE)
```
```{r}
colnames(post_df1)
```

```{r}
post_df1 %>% 
  dplyr::select(creator_username,createdAt,impressions,upvotes,body)
```

## Get all Posts with a certain Hashtag

Because there are thousands of posts, we time out the request after a certain amount of seconds.

```{r,message = F,warning = F}
hashtag_posts_df1 <- 
  parler_hashtag(hashtag = "nocovidvaccine",
                 output_format = "data.frame",
                 flatten_sep = " || ",
                 parse_numbers = TRUE,
                 verbose = TRUE,
                 timeout = 60)
```

```{r}
colnames(hashtag_posts_df1)
```

```{r}
hashtag_posts_df1 %>% 
  head(50) %>% 
  dplyr::select(creator_username,createdAt,impressions,upvotes,body)
```


## Get User Profile Data

### Raw JSON String

NOT WORKING YET, FIX TOMORROW!

```{r,eval = F}
json_str <- 
  parler_profile(user = "TuckerCarlson",
                 output_format = "json",
                 flatten_sep = " || ",
                 verbose = FALSE)
```


### R data.frame (nested variables flattened)

```{r}
out <-
  parler_profile(user = "caseybmulligan",
                 output_format = "data.frame",
                 flatten_sep = " || ",
                 token_variables = F,
                 parse_numbers = TRUE,
                 verbose = TRUE)

```

```{r}
colnames(out)
```

```{r}
out %>% 
  select(name,username,followers,following,likes,posts,joined,bio)
```
### Without Token-associated variables 

```{r}
out2 <-
  parler_profile(user = "caseybmulligan",
                 output_format = "data.frame",
                 flatten_sep = " || ",
                 token_variables = TRUE,
                 parse_numbers = TRUE,
                 verbose = TRUE)
```

```{r}
colnames(out2)
```

New colnames which are only outputtet if `token_variables == TRUE`:

```{r}
colnames(out2) %>% .[!. %in% colnames(out)]
```

### JSON List Object

```{r}
jlist <- 
  parler_profile(user = "caseybmulligan",
                 output_format = "list",
                 flatten_sep = " || ",
                 verbose = FALSE)
```

```{r}
str(jlist)
```


### Multiple Users

```{r}
user_vec <- c("Marklevinshow","SeanHannity","Devinnunes","GovernorNoem",
              "KTHopkins","Westmonster","TommyRobinson")

out_df <- 
  purrr::map(.x = user_vec,
           .f = ~ 
             parler_profile(user = .x,
                            output_format = "data.frame",
                            flatten_sep = " || ",
                            token_variables = FALSE,
                            parse_numbers = TRUE,
                            verbose = FALSE)
           ) %>% 
  bind_rows()

```

```{r}
out_df %>% 
    select(name,username,followers,following,likes,posts,joined,bio)
```

